Pulmonary rehabilitation Robot Follower

### 2020-02-19 alpibot.tex
Upload a new version with more references on the introduction.

Robotics applications can offer a solution in this scenario.

@@

Tethered robots, on the other hand, have been extensively research in robotics communities.  They offered a very simple solution to some common navigation problems, and they can be very effective on robot-to robot interaction or while interacting with humans in Human Robot Interfaces, collaborative robotics~\cite{Rekleitis2001,Hirata2009}.

@@

The medical community is frequently skeptical to technological solutions for medical personel (REF).  At the same time, development process as design thinking and other similar tendencies prioritize rapid development, prototyping that can bring quickly feedback from real users about the drawbacks and improving opportunities.  In this context, it is important to perform rapid prototyping.

>>>>

Robotics applications can offer a solution in this scenario.  Ground Service Robot in a person following scenario.

UGVs

@@

Tethered robots, on the other hand, have been extensively research in robotics communities.  They offered a very simple solution to some common navigation problems, and they can be very effective on robot-to robot interaction or while interacting with humans in Human Robot Interfaces, collaborative robotics~\cite{Rekleitis2001,Hirata2009,Ferrin2010}.

Person follower \cite{Islam2019}

@@

The medical community is frequently skeptical to technological solutions for medical personel~\cite{Gaggioli2006,Fasola2012,Cherubini2008,Wolpaw2012BraincomputerIP}.  At the same time, development process as design thinking and other similar tendencies prioritize rapid development, prototyping that can bring quickly feedback from real users about the drawbacks and improving opportunities.  In this context, it is important to perform rapid prototyping.
